Depression and suicidality as credible signals of need

### 2021-05-23 Paper.rmd
Added a toc and css file

---
title: "Depression and suicidality as credible signals of need"
author: "Michael R. Gaffney, Kai Adams, Kristen L. Syme, and Edward H. Hagen"
date: '`r format(Sys.Date(), "%B %d, %Y")`'
always_allow_html: false
output: 
  bookdown::html_document2:
    toc: true
    number_sections: false
bibliography: MTBib.bib
csl: apa-6th-edition.csl
---

>>>>

---
title: "Depression and suicidality as credible signals of need"
author: "Michael R. Gaffney, Kai Adams, Kristen L. Syme, and Edward H. Hagen"
date: '`r format(Sys.Date(), "%B %d, %Y")`'
always_allow_html: false
output:
  bookdown::html_document2:
    toc: true
    toc_float: true
    collapsed: false
    number_sections: false
    css: style.css
bibliography: MTBib.bib
csl: apa-6th-edition.csl
---
